How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2020-12-15 analysis/paper/paper.Rmd
add N arrow, scale, inset map to site map

---
title: "How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?"
author:
  - Author Gayoung Park
  - Author Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2: 
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Human behavioural ecological models use stone artefacts as a source of information for understanding forager mobility. We use these models to examine stone artefacts from 22 sites in Korea to investigate mobility and site occupation during the Late Pleistocene. This study focuses on two questions: how did the introduction of stemmed points change forager' mobility and landscape use? And how did this new technology change the way people use habitation sites? We analyse artefact volumetric density, retouch frequency, composition of toolkits, artefact raw materials, environmental and demographic contexts. Quartz and side scrapers, in addition to cores and choppers, remain dominant in assemblages before and after the introduction of stemmed points throughout the Late Pleistocene. Our results show that forager groups using stemmed points were associated with occupation of marginal or extreme environments. In addition, groups with stemmed points were associated with expedient technologies indicating residential and less mobile behaviours. The environmental context of this technological innovation was a gradual decrease in temperature into the LGM. A population increase followed after the appearance of stemmed points.

>>>>

---
title: "How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?"
author:
  - Gayoung Park
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2: 
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Human behavioural ecological models use stone artefacts as a source of information for understanding forager mobility. We use these models to examine stone artefacts from 22 sites in Korea to investigate mobility and site occupation during the Late Pleistocene. This study focuses on two questions: how did the introduction of stemmed points change forager' mobility and landscape use? And how did this new technology change the way people use habitation sites? We analyse artefact volumetric density, retouch frequency, composition of toolkits, artefact raw materials, environmental and demographic contexts. Quartz and side scrapers, in addition to cores and choppers, remain dominant in assemblages before and after the introduction of stemmed points throughout the Late Pleistocene. Our results show that forager groups using stemmed points were associated with occupation of marginal or extreme environments. In addition, groups with stemmed points were associated with expedient technologies indicating residential and less mobile behaviours. The environmental context of this technological innovation was a gradual decrease in temperature into the LGM. A population increase followed after the appearance of stemmed points.
